% budget.tex
% defs for below.  note " " after defs.
\def\piA{David J. Lilja}
\def\numRAs{2}
\def\pilist{PI: \piA}
\def\thisyear{2012}
\def\startdate{09/02/2012}
\def\enddate{09/01/2012}
\def\phdstipend{\$2,125/mo }
\def\mscstipend{\$1,940/mo }
\def\studraise{4\% }
\def\salaryallocationrate{8.34\%} % no trailing space
\def\employeebenefitrate{27.0\% }
\def\vacationaccrualrate{9.5\% }
\def\networkservicescost{\$100/person/month }
\def\networkfacilitycharges{\$150/person/month} % no trailing space
\def\MITninemonthtuition{\$33,400} % no trailing space
\def\MITtuitioninflator{4\% }
\def\MITtuitionsubsidy{45\% }
\def\MITtuitioncharge{55\% }
\def\msAllocation{1.24\%}
\def\facostinception{07/01/2006} % no trailing space
\def\facostrate{65\% }

% make the outer enumerated list alpha A, B, C ...
\renewcommand{\theenumi}{\Alph{enumi}}
\renewcommand{\theenumii}{\arabic{enumii}}

\vspace*{1.0in}
\begin{center}
{\large
UMN / ARTiC Laboratory \\
\pilist \\
Proposed Budget Period: \startdate -- \enddate \\
Budget Justification for Cost Proposal
}
\end{center}

\begin{enumerate}

%A
\item \underline{Key Personnel:}

\begin{tabular}{|l|l|} \hline
\underline{Last Name} & \underline{Review/Raise} \\ \hline
\piA & June \\ \hline
\end{tabular}

MIT fully supports the academic year salaries of professors, associate
professors, and assistant professors, but makes no specific commitment
of time or salary to any individual research project.

%B
\item \underline{Other Personnel:}

\begin{enumerate}
  \item \underline{Research Assistants:} \\{~}\\
100\% of the stipend is charged to the research project. The RA stipend
is not subject to employee benefits. Stipend for the year beginning on
\startdate is \phdstipend for a PhD student and \mscstipend for a
Masters student. A \studraise raise is applied each year (in June).

%2
  \item \underline{Other (Technical \& Administrative Support):}\\{~}\\
The Computer Science Artificial Intelligence Laboratory (CSAIL) provides administrative
services for all principal investigators who submit proposals through CSAIL. These
administrative services are run by the Headquarters Staff and include Fiscal, Personnel,
Facilities and other CSAIL operations.\\{~}\\
These services are supported by an Allocated Project Level Cost, which is assessed against all
contracts and grants. The current rate for the Salary Allocation is \salaryallocationrate. The Allocation
Base is shown below:

\begin{tabular}{|c|c|c|c|} \hline
Allocation & Year 1 & Year 2 & Year 3 \\ \hline
Base & \$XXX,YYY & \$XXX,YYY & \$XXX,YYY \\ \hline
\end{tabular}

\end{enumerate}

\item \underline{Fringe Benefits}

\begin{enumerate}

%(a)
\item Employee benefits are calculated at the rate of \employeebenefitrate and 
are applied to total salary expenses, less Research Assistants.

\item Vacation accruals are calculated at the rate of \vacationaccrualrate and 
are applied to total salary expenses, less Faculty and Research
Assistants.

\end{enumerate}

%D
\item \underline{Travel:}

\begin{enumerate}

\item \underline{Domestic Travel:}

\item \underline{Foreign Travel:}

\end{enumerate}

\item \underline{Other Direct Costs:}

\begin{enumerate}

\item \underline{Material \& Supplies:}\\{~}\\
Estimated costs for software and supplies needed for the project.

\item \underline{Computer Services:}\\{~}\\
MIT/CSAIL has a centralized network services function. The costs consist of Network Services at
\networkservicescost and Network Facility Charges at \networkfacilitycharges. The base number of
people used for this calculation was \numRAs (the two full time RAs).

\item \underline{Other:}\\{~}\\
(a) RA tuition: For the academic year starting \thisyear, MIT 9-month
tuition is \MITninemonthtuition. A \MITtuitioninflator annual inflator
is applied each year. MIT will subsidize \MITtuitionsubsidy of tuition,
leaving \MITtuitioncharge to be charged to the project. During the
summer, MIT has waived tuition.\\{~}\\ 
(b) Allocated expenses are assessed against all contracts and
grants. The current rate for the Materials and Services Allocation is
\msAllocation. These funds help support the Headquarters staff mentioned
above in the section entitled ``Other (Technical \& Administrative
Support)''. Please see the table in that section for the allocation
base.

\item \underline{Equipment:}

The equipment line items will support purchases as follows:

\begin{itemize}

\item Year One (\$X,XXX): enter purpose, items and costs here

\item Year Two (\$X,XXX): enter purpose, items and costs here

\item Year Three (\$X,XXX): enter purpose, items and costs here

\end{itemize}

\item \underline{[Describe any other direct cost items here]:}

\end{enumerate}

\item \underline{Indirect Costs (Facilities \& Administrative Costs):}\\{~}\\
Effective \facostinception, F\&A Costs are calculated by applying the
negotiated rate of \facostrate to the Modified Total Direct Cost (MTDC)
base. The MTDC base includes all direct costs, except Graduate Student
Tuition, Network Facilities Charges, the Salary Allocation (and
associated benefits), and the Materials and Services Allocation.

\end{enumerate}
